### 2021-02-13 main.tex
komenty; presun eq:model_cost

Given a problem $P$, a symbol cost model $c : \cnf \to \re^*$
\todo{Confusing?}
returns a vector of costs of the symbols of $P$:
$$
c(P) = (c_1, \ldots, c_n)
$$

Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
The symbol cost model $c$ can be extended to a precedence cost model $C$
by taking the weighted sum of symbol costs:
$$
C(\Prec | P)
= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
= k(n) \DotProd{c(P)}{\inv{\Prec}}
$$
Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
\todo{Discuss, prove.}

Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
ensures that costs of precedences of various lengths are commensurable.
Observe namely that if $c$ assigns each symbol the same cost $c_0$,
then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
\begin{equation} \label{eq:model_cost}
C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
\end{equation}

>>>>

Given a problem $P$, a symbol cost model 
\todo{MS: Zvidavy invalida Jirka Karasek: a co ze je to ten model? 
Mohl byste to to prosim nekde driv vysvetlit?}
$c : \cnf \to \re^*$
\todo{MS: Mozna by se dalo zbavit lehce podivneho $\re^*$ tim,
ze model bude funkce $(P \in \cnf, s \in \Sigma_P) \to \re$?
Zas pak nepujde pouzivat zapis skalarniho soucinu; hmmm.}
returns a vector of costs of the symbols of $P$:
$$
c(P) = (c_1, \ldots, c_n)
$$

Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
The symbol cost model $c$ can be extended to a precedence cost model $C$
by taking the weighted sum of symbol costs:
\begin{equation} \label{eq:model_cost}
C(\Prec | P)
= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
= k(n) \DotProd{c(P)}{\inv{\Prec}}
\end{equation}
Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
\todo{Discuss, prove.}

Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
ensures that costs of precedences of various lengths are commensurable.
Observe namely that if $c$ assigns each symbol the same cost $c_0$,
then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
$$
C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
$$
